Semi-inclusive deep-inelastic scattering in Wandzura--Wilczek-type approximation

### 2019-04-11 arxiv2/test-WW-type-v2F.tex
AP

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering \ 
\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
\includegraphics[width=0.8\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
\caption{\label{aulsinphi_jlab}
	$A_{UL}^{\sin\phi_h}$ for proton vs.~$x$ from WW-type
	approximation in comparison to data for the following hadrons.
	Upper panel left: $\pi^\pm$ from HERMES \cite{Airapetian:2005jc}.
	Upper panel right: $\pi^0$ from HERMES (blue) \cite{Airapetian:2001eg}
	and JLab (red) \cite{Jawalkar:2017ube}.
	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2018ovx,Parsamyan:2018evv}.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\centering
\begin{tabular}{cc} \ \hspace{-8mm}
\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} &
\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
{\tiny (a) }&{\tiny (b)} \\
\includegraphics[width=0.6\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}&
\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf}\\
{\tiny (c) \hspace{3cm} (d)}&{\tiny (e)}
\end{tabular}
	\caption{\label{aulsinphi_jlab} 
	$A_{UL}^{\sin\phi_h}$ for proton vs.~$x$ from WW-type
	approximation and comparison to the data.
	$\pi^\pm$ from HERMES \cite{Airapetian:2005jc} (a), $\pi^0$ from HERMES (blue) \cite{Airapetian:2001eg} and JLab (red) \cite{Jawalkar:2017ube} (b), 
	preliminary COMPASS data
	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (c,d),  
	and our calculation for COMPASS kinematics in 
	WW-type approximation (e)
	\ps{shown separately for reasons explained in the
	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
